Sequential algorithms to split and merge ultra-high resolution 3D images

### 2017-08-11 paper.tex
Updates following discussion with @Yongpinggao

@@

>>>>

implemnted on-the-fly compression using Python's gzip library. Use
gzip open file. We don't need on-the-fly compression for multiple
reads. gzip can find the seek point but it still has to decompress
everything before the seek point. Cluster reads would be very
penalized by that. Multiple reads wouldn't care. Same conclusions for
splitting.

indexed gzip would seek faster (improve the seekk time) but
decompression time would remain (still have to decompress from
begining of file).

if we wanted cluster reads to work well with on the fly compression,
we would need to investigate techniques like~\cite{rajna2015speeding}

@@

\subsection{Compression}

Naive blocks, naive slices, cluster reads and multiple reads at 3, 6,
9, 12, 16GB, on SSD, with on-the-fly compression (graph will also show
without compression (previous results)) for comparison.
